A Real-Time Sonar Simulator for Automatic Target Recognition

### 2015-07-22 Simulator/article.tex
la2pdf commit - 2015:07:22	14:08:05	(Wed22.Jul)

\begin{figure}[p]\centering%
\subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
\graphicsAI[drawing,width=\linewidth]{gfx/data_cylinder_submerged.svg}%
\label{data_cylinder}}%
\subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
\graphicsAI[drawing,width=\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\label{sim_cylinder}}%
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure}

@@

\begin{figure}[p]\centering%
\subfloat[Best template out of a predefined set. Inaccurate cylinder length, alignment and immersion depth. The segmented shadow and highlight regions are misaligned.]{
\graphicsAI[drawing,width=\linewidth]{gfx/overlay_cylinder_submerged.svg}%
\label{overlay_cylinder}}%
% \hfil%
\subfloat[Adapted template. Template simulated with adapted parameters. Good fit in both highlight and shadow segments.]{%
\graphicsAI[width=\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
\label{overlay_cylinder_adaptive}}%
\hfill\parbox{\linewidth}{\small\centering
Segmentation overlay color description:\\[.5\baselineskip]
\begin{minipage}{\linewidth}
\cdesc{800000}{Template highlight and image highlight}
\cdesc{FF1000}{Template highlight only}
\cdesc{FFEB00}{Image highlight only}
\cdesc{83FF7C}{Background pixels}
\end{minipage}%
\begin{minipage}{\linewidth}
\cdesc{000083}{Template shadow and image shadow}
\cdesc{0014FF}{Template shadow only}
\cdesc{00EFFF}{Image shadow only}
\cdesc{00A7FF}{Template shadow and image highlight}
\end{minipage}}
\vspace{\baselineskip}
\caption{Segmented simulation image overlaid the segmented SAS image.}
\end{figure}

>>>>

What's going on?

\begin{figure*}[h]\centering%
\subfloat[SAS image of a cylinder with 2.6\;m length and 0.53\;m radius.]{%
\graphicsAI[drawing,width=0.5\linewidth]{gfx/data_cylinder_submerged.svg}%
\label{data_cylinder}}%
\subfloat[Cylinder simulation with parameters estimated from SAS image: Length 2.6\;m, burial depth 0.263\;m, aspect angle 105$^\circ$.]{
\graphicsAI[drawing,width=0.5\linewidth]{gfx/sim_cylinder_submerged_adaptive.svg}%
\label{sim_cylinder}}%
\caption{A SAS image of a cylinder and a template simulation adapted to it.}
\end{figure*}

@@

BS!!!

\begin{figure*}[!tb]\centering%

\subfloat[Best template out of a predefined set. Inaccurate cylinder length, alignment and immersion depth. The segmented shadow and highlight regions are misaligned.\label{overlay_cylinder}]{
\graphicsAI[drawing,width=.5\linewidth]{gfx/overlay_cylinder_submerged.svg}%
}%
% % \hfil%
\subfloat[Adapted template. Template simulated with adapted parameters. Good fit in both highlight and shadow segments.\label{overlay_cylinder_adaptive}]{%
\graphicsAI[width=.5\linewidth]{gfx/overlay_cylinder_submerged_adaptive.svg}%
}%
\subfloat[][...]{hmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmm}
% \parbox{1cm}{HMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMMmmmmmmmmmmmmmmmmmmmm}
% \hfill
% 
% % \newline
% \raggedright
% \mbox{\parbox{1cm}{\small\centering
% HMmmmmmmmmmmmmmmmmmm mmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmmm
% % Segmentation overlay color description:\\[.5\baselineskip]
% % \begin{minipage}{.49\linewidth}
% % \cdesc{800000}{Template highlight and image highlight}
% % \cdesc{FF1000}{Template highlight only}
% % \cdesc{FFEB00}{Image highlight only}
% % \cdesc{83FF7C}{Background pixels}
% % \end{minipage}%
% % \begin{minipage}{.49\linewidth}
% % \cdesc{000083}{Template shadow and image shadow}
% % \cdesc{0014FF}{Template shadow only}
% % \cdesc{00EFFF}{Image shadow only}
% % \cdesc{00A7FF}{Template shadow and image highlight}
% % \end{minipage}
% }
% \vspace{\baselineskip}
% \caption{Segmented simulation image overlaid the segmented SAS image.}
\end{figure*}
